Marine Conservation In Fishing Effort Markets

### 2019-05-22 docs/old_ms/PIPA_Palau_Science_JL.tex
Updated MS for John and Chris

\begin{sciabstract}
Our oceans are becoming increasingly crowded and privatized as different activities compete for space. Marine Protected Areas have the primary objective of conserving bounded waters by displacing or limiting fishing effort. With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered. A spatial closure in a vessel-day-managed fishery can potentially result in large costs to the implementing country, which might deter conservation efforts. We show that effort markets may reduce up to 70\% of the costs, and that allocation rules based on biomass (rather than effort) may incentivize conservation. We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented implemented in 2015 in Kiribati) had on vessel distribution and behavior. Aggregate fishing effort remains relatively constant following the closure, but is significantly reduced within Kiribati, especially by vessels that historically fished within PIPA before its implementation. We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displacing fishing effort. We use these insights predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually. Our work highlights the role of effort markets in enabling conservation, and the importance of allocation rules that praise, not punish, conservation. The Parties to the Nauru Agreement have successfully managed their fishery and developed a management scheme that allows for conservation interventions to come at a low cost.
\end{sciabstract}

@@

Displacement or elimination of fishing effort within the protected area might come at a cost when fisheries are managed under an effort market. For example, tuna purse seine fisheries in the Pacific are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA; Figure \ref{fig:PNA_map}). The agreement regulates the access of foreign fishing vessels to PNA waters, and control the allocation and sales of 45,000 vessel-days. Holding 80\% of historical skipjack tuna purse seine grounds within their joint Exclusive Economic Zones (EEZ; with surface area of  14.6 million km\textsuperscript{2}), PNA countries have achieved greater bargaining power \cite{havice_2010}; vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors. The revenue from access fees may represent up to 50\% of government revenue for some of the parties.

The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas on earth. Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2}, about 11\% of Kiribati's EEZ or 2.7\% of total PNA area, effectively displacing all fishing effort within it \cite{mcdermott_2018,mccauley_2016}. A pressing question is that of the costs associated to the displacement of fishing effort and possible revenue losses from the fishing license sales. While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs, like Palau's 80\% closure to go into effect in 2020 \cite{cimino_2019}.

@@

We begin by simulating a spatial closure in a world where vessel-days can not be traded between countries. A spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portions of the Patch (Fig. \ref{fig:PNA_model}A). The losses are caused by a drop in vessel-day prices for Patch 1, which results from a lower portion of the stock being available for harvest (Fig. \ref{fig:vessel_day_price_no_trading_plot}). Costs increase with reserve size ($R$), and decrease as within-patch movement ($\theta$) increases. Given the non-linear costs ($\beta > 1$), the closure-to-cost ratio can be greater than 1:1 if within-patch movement is low (\emph{i.e.} $\theta < 0.2$). The spatial closure in Patch 1 results in moderate increases in revenue for Patches 2 - 9 (Fig. \ref{fig:profits_PNA_notKIR_no_trading_plot}). When countries do not trade between them, the costs of conservation are large and incurred by Patch 1, but the benefits perceived by the eight other patches. Importantly, the increases in revenue to other patches do not compensate for the total losses to Patch 1.

The objective of a VDS is to allow for trading between parties and achieve the optimal distribution of effort in relation to fish distribution. In the case of the PNA, for example, spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}. Vessels redistribute across PNA countries as they track fish, and tradable permits reduce costs to the parties \cite{aqorau_2018}. We explore the effect of a spatial closure in Patch 1, but now allow for vessel-days to be traded between Patches. Patch-level demand for vessel days is governed by the fishable stock size (\emph{i.e.} biomass not within the reserve). Trading occurs until vessel-day prices are the same across patches, given a total allowable effort (\emph{i.e.} 45,000 vessel-days) is reached. Here, costs from a closure in Patch 1 are significantly reduced by trading (Fig. \ref{fig:PNA_model}B-C). In this case, surplus of vessel-days in Patch 1 are sold to Patches 2 - 9. Vessel-day prices are constant across patches and lower than when there is no reserve, but still higher than when no trading is allowed (Fig. \ref{fig:vessel_day_price_with_trading_plot}). By optimally trading vessel-days, the cost to the implementing country can be reduced as much as 97\%.

Our previous analyses estimate loss in revenue from effort displacement. Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass. In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ. \footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}. Trading vessel-days to other countries would imply that historical within-patch effort declines through time. The allocated days to the Patch with the spatial closure would eventually be reduced to the 40\% depending on biomass.

We explore the effect that allocation rules have through time when trading is allowed by projecting the fishery 50 years into the future with. We used a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently to update annual allocations based on a seven-year running mean of these measures. Costs are greater when allocation is based only on patch-level historical effort (\emph{i.e.} $\alpha = 1$; Fig. \ref{fig:allocation_cost_plot}). However, costs can be significantly reduced when trading is allowed if allocation is based on historical biomass instead. When there is no trading, patch-level effort remains unchanged, and since any growth in stock is equally distributed across patches, allocation rules do not affect costs in a case without trading.

@@

Annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018, mainly due to displaced vessels allocating less time to Kiribati (Fig. \ref{fig:all_PS_VDS_year}B); Fig. \ref{fig:hist_kir_fishing}). Current effort in Kiribati waters are well below their 11,000 vessel-day allocation \cite{yeeting2018stabilising}. However, we observe a relatively constant 45,000 vessel-days at the PNA-level, suggesting that Kiribati is, in fact, able to trade vessel-days and reduce the costs of displacement. The spatial redistribution patterns of displaced vessels relative to non-displaced vessels are shown in Figure \ref{fig:fishing_raster_diff}.

We complement our analysis of change in observed vessel-days by looking at country-level data reported by the Pacific Islands Forum Fisheries Agency (FFA). We find that Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD. Total PNA revenues showed a net increase of \$28 million USD (Fig. \ref{fig:total_PNA_revenues}). The largest decrease was observed for Kiribati, while the largest increase was also observed for Papua New Guinea.

Total fishing effort in the PNA increased between 2015 and 2016, but fishing area decreased due to PIPA implementation (Fig. \ref{fig:all_PS_VDS_year}). We inspect the crowding effects that may arise by applying more (or the same amount of) fishing effort over less fishing area with two indices of spatial overlap between displaced and non-displaced vessels: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month. The two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig. \ref{fig:sp_corr}). The number of cells with presence from both fleets and spatial correlation increase by a factor of four and three, respectively. Crowding might be driven by environmental variation concentrating fish at specific locations, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementaiton. We observe similar patterns when repeating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).

@@

On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act. Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80 percent of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world, effectively displacing all effort within its waters (Fig. \ref{fig:plw_2018} shows longline and purse seine fishing effort within PNMS for 2018). As part of the Nauru Agreement, Palau receives 700 purse seine vessel-days each year. They also  use a vessel-day scheme to manage the longline fishery  (10,500 vessel-days per year). Unlike the purse seine vessel days, longline vessel-days are not tradable within countries and are worth a fraction, at about \$200 USD each. Our previous analyses suggest that Palau should be able to lessen the costs of the closure by trading purse seine vessel-days (\$5.65 - \$8.75 million USD) with other PNA members, but might lose more than 50\% of the revenues from the longline vessel-days (\$2.1 million USD).

Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios. In Scenario Palau retains its current allotment of purse seine vessel-days and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day). In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day). Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days. It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as purse seine effort in its EEZ eventually reaches zero. In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively. In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish. The longline vessel day loss is calculated using an average value of \$200 for 10,500 days. The export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).

@@

Our findings provide insights into the effect that LSMPAs can have on redistribution of fishing effort and change in behavior. Our analyses predicts losses in revenue to countries that implement a spatial closure. However, these losses can be significantly reduced by market instruments and biomass-based allocation rules. Using vessel tracking data, we see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also other PNA countries and the high seas. Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onward. Redistribution lead to a crowding effect, and the spatial closure had little effect on the \emph{total} fishing effort exerted by purse seiners, but vessel-level responses were heterogeneous. Our analysis suggests that losses would be expected for Palau's Marine Sanctuary, but that these can be minimized if effort is traded freely and allocations are based in biomass, not effort. Here, we discuss the implications of our findings and possible shortcomings in our analysis.

@@

ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}. We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation. For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu. However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}). Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself it does not explain the observed patterns. While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.

A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guides the decision-making process of vessel captains. Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact. Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions or between countries or detailed vessel-day prices.

Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights. The closure caused a crowding effect, which causes some vessels to redistribute to areas close by. The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}. Overlaying conservation interventions over existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs. Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.

>>>>

\begin{sciabstract}
Marine Protected Areas have the primary objective of conserving bounded waters by displacing or limiting fishing effort. With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered. A spatial closure in a trans-boundary fishery can potentially result in costs to the implementing country and benefits to neighboring countries. We show that effort markets may reduce up to 70\% of the costs of Marine Protected Areas, and that allocation rules based on biomass (rather than effort) may further incentivize conservation. We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented in 2015 in Kiribati) had on vessel distribution and behavior. Aggregate fishing effort remains relatively constant following the closure, but is significantly reduced within Kiribati, especially by vessels that historically fished within PIPA before its implementation. We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displaced fishing effort. We use these insights to predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate that effort markets could reduce the cost of implementation by as much as 77\%. Our work highlights the role of effort markets in enabling conservation, and the importance of allocation rules that praise, not punish, conservation. The Parties to the Nauru Agreement have successfully developed a management scheme that allows for conservation interventions to come at a low cost, and could be a model for trans-boundary conservation across the globe.
\end{sciabstract}

@@

Displacement or elimination of fishing effort within the protected area might come at a cost to the implementing party when fisheries are managed under an effort market (i.e. fishing rights are sold to firms). For example, tuna purse seine fisheries in the Pacific are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA; Figure \ref{fig:PNA_map}). The agreement regulates the access of foreign fishing vessels to PNA waters, and control the allocation and sales of 45,000 ``vessel-days'': the right for one vessel to fish for one day in a country's waters. Holding 80\% of historical skipjack tuna purse seine grounds within their joint Exclusive Economic Zones (EEZ; with surface area of  14.6 million km\textsuperscript{2}), PNA countries have achieved greater bargaining power by working together \cite{havice_2010}; the vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors. The revenue from fisheries access fees represents up to 50\% of government revenue for some of the PNA countries.

The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas on earth. Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2}, about 11\% of Kiribati's EEZ or 2.7\% of total PNA area, effectively displacing all fishing effort within it \cite{mcdermott_2018,mccauley_2016}. A pressing question is that of the costs associated with the displacement of fishing effort and possible revenue losses from vessel-day sales. While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs, like Palau's 80\% closure to go into effect in 2020 \cite{cimino_2019}.

@@

We begin by simulating a spatial closure in a setting where vessel-days can not be traded between countries. A spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portions of the Patch (Fig. \ref{fig:PNA_model}A). The losses are caused by a drop in vessel-day prices for Patch 1, which results from a lower portion of the stock being available for harvest (Fig. \ref{fig:vessel_day_price_no_trading_plot}). Costs increase with reserve size ($R$), and decrease as within-patch movement ($\theta$) increases. Given the non-linear costs ($\beta > 1$), the closure-to-cost ratio can be greater than 1:1 if within-patch movement is low (\emph{i.e.} $\theta < 0.2$). The spatial closure in Patch 1 results in moderate increases in revenue for Patches 2 - 9 (Fig. \ref{fig:profits_PNA_notKIR_no_trading_plot}). When countries can not trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches. Importantly, the increases in revenue to the other patches do not compensate for the total losses to Patch 1.

The objective of a VDS is to allow for trading between parties and achieve the optimal distribution of effort in relation to fish distribution. In the case of the PNA, for example, spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}. Vessels redistribute across PNA countries as they track fish, and tradable permits reduce costs to the parties by allowing them to sell surplus vessel-days to be used in the EEZ of another country \cite{aqorau_2018}. We explore the effect of a spatial closure in Patch 1, but now allow for vessel-days to be traded between Patches. Patch-level demand for vessel days is governed by the fishable stock size (\emph{i.e.} biomass not within the reserve). Trading occurs until vessel-day prices are the same across patches, given a total allowable effort (\emph{i.e.} 45,000 vessel-days) is reached. Here, costs from a closure in Patch 1 are significantly reduced by trading (Fig. \ref{fig:PNA_model}B-C). In this case, the surplus of vessel-days in Patch 1 are sold to Patches 2 - 9. Vessel-day prices are constant across patches and lower than when there is no reserve, but still higher than when no trading is allowed (Fig. \ref{fig:vessel_day_price_with_trading_plot}). By optimally trading vessel-days, the cost to the implementing country can be reduced as much as 97\%.

Our previous analysis predicts a loss in total revenue from effort displacement. Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass. In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time. The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.

We explore the effect that allocation rules have through time when trading is allowed by projecting the fishery 50 years into the future. We used a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently to update annual allocations based on a seven-year running mean of these measures. Costs are greater when allocation is based only on patch-level historical effort (\emph{i.e.} $\alpha = 1$; Fig. \ref{fig:allocation_cost_plot}). However, costs can be significantly reduced when trading is allowed if allocation is based on historical biomass instead. When there is no trading, patch-level effort remains unchanged, and since any growth in stock is equally distributed across patches, allocation rules do not affect costs.

@@

Annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018, mainly due to displaced vessels allocating less time to Kiribati (Fig. \ref{fig:all_PS_VDS_year}B, Fig. \ref{fig:hist_kir_fishing}). Current effort in Kiribati waters is well below their 11,000 vessel-day allocation \cite{yeeting2018stabilising}. However, we observe a relatively constant 45,000 vessel-days at the PNA-level, suggesting that Kiribati is, in fact, able to trade vessel-days and reduce the costs of displacement. The spatial redistribution patterns of displaced vessels relative to non-displaced vessels are shown in Figure \ref{fig:fishing_raster_diff}.

We complement our analysis of change in observed vessel-days by looking at country-level data reported by the Pacific Islands Forum Fisheries Agency (FFA). We find that Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD. Total PNA revenues showed a net increase of \$28 million USD (Fig. \ref{fig:total_PNA_revenues}). The largest decrease was observed for Kiribati, while the largest increase was observed for Papua New Guinea.

Total fishing effort in the PNA increased between 2015 and 2016, but fishing area decreased due to PIPA implementation (Fig. \ref{fig:all_PS_VDS_year}). We inspect the crowding effects that may arise by applying more (or the same amount of) fishing effort over less fishing area with two indices of spatial overlap between displaced and non-displaced vessels: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month. The two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig. \ref{fig:sp_corr}). The number of cells with presence from both fleets and spatial correlation increase by a factor of four and three, respectively. Crowding might be driven by environmental variation concentrating fish at specific locations, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementaiton. We observe similar patterns when repeating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).

@@

On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act. Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80 percent of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world, effectively displacing all effort within its waters (Fig. \ref{fig:plw_2018} shows longline and purse seine fishing effort within PNMS for 2018). As part of the Nauru Agreement, Palau receives 700 purse seine vessel-days each year. They also  use a vessel-day scheme to manage the longline fishery  (10,500 vessel-days per year). Unlike the purse seine vessel-days, longline vessel-days are not tradable across countries and are worth much less, at about \$200 USD each. Our previous analyses suggest that Palau should be able to lessen the costs of the closure by trading purse seine vessel-days (\$5.65 - \$8.75 million USD) with other PNA members, but might lose more than 50\% of the revenues from the longline vessel-days (\$2.1 million USD).

Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios. In Scenario 1, Palau retains its current allotment of purse seine vessel-days and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day). In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day). Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days. It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as purse seine effort in its EEZ eventually reaches zero. In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively. In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is currently planning on banning the export of fish. The longline vessel day loss is calculated using an average value of \$200 for 10,500 days. The export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).

@@

Our findings provide insights into the effect that LSMPAs can have on the redistribution of fishing effort and changes in behavior. Our analyses predict losses in revenue to countries that implement a spatial closure. However, these losses can be significantly reduced by market instruments and biomass-based allocation rules. Using vessel tracking data, we see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also to other PNA countries and the high seas. Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onward. Redistribution leads to a crowding effect, and the spatial closure has little effect on the \emph{total} fishing effort exerted by purse seiners, but vessel-level responses were heterogeneous. Our analysis suggests that losses would be expected for Palau's Marine Sanctuary, but that these can be minimized if effort is traded freely and allocations are based on biomass, not effort. Here, we discuss the implications of our findings and possible shortcomings in our analysis.

@@

ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}. We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation. For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu. However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}). Our analysis shows that sea surface temperature variation does have an effect on our crowding and behavioral outcomes, but that by itself it does not explain the observed patterns. While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.

A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guides the decision-making process of vessel captains. Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact. Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions between countries or detailed vessel-day prices.

Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights. The closure caused a crowding effect, which seems to lead some vessels to redistribute to areas close by. The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}. Overlaying conservation interventions and existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs. Furthermore, implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
